Modeling Two-Dimensional Vesicle Hydrodynamics with Hydrophobic Attraction Potential Simulations

### 2021-08-18 doc/main_jfm.tex
updates

Following the relaxation experiments of the Janus-vesicle, this section will focus on the behavior of 
Janus-vesicles under flows. To extract physical quantities of the target structure using the proposed model, 
the scaling laws and the dimensionless units are given as follows.
The length unit is scaled by the length of phospholipids $l=2.5$ nm which is set as the diameter of each 
Janus particle. The force is scaled from the interfacial tension $\gamma=4.11$ pN nm$^{-1}$ 
from ~\cite{Ryham16}. We then be able to calculate the characteristic time scale 
$\tau = \mu l/\gamma = 0.61$ ns where the fluid viscosity $\mu=1$ cP. With the same framework, \cite{Fu20} provides the bending rigidity $\kappa=8.51$ $k_BT$.
%
For the model parameters, the decay length of attraction $\rho = 2l = 5$ nm, the repulsion length scale is 
$\rho_0=0.5$, and teh repulsion strength $M=4.0$.
The dimensionless shear rate is given by $\chi = \dot\gamma \tau$ where $\dot\gamma$ is the shear rate.

@@

To study the deformation of a Janus-vesicle under a shear flow using the proposed algorithm, 
we adopt a widely tested numerical simulation in both continuum and molecular dynamics models, single vesicle under a shear flow. The well known results indicate that the vesicle has tank-treading behavior when 
there is no viscosity contrast in both inside and outside of the vesicle that is one of the features in the  framework of the proposed model.

The centroid of the pre-relaxed $58$-body Janus vesicle is initially placed at the origin then the shear flow 
with a certain shear rate $\chi$ is turned on. 
The snapshots of the simulation for single vesicle in a shear flow with a shear rate $\chi=0.0025$ are shown 
in Figure~\ref{figure3}.
Panels (a)-(b) show the initial shape obtained from the relaxation run and the deformed 
configuration of the Janus-vesicle after a period of time ($t=4000$) is in panels (c)-(d). 
The background color in panels (a) and (c) presented in the figure is the strength of the action due to the
hydrophobic attraction. From weak to strong action field, the color varies from blue to red. Clearly, the
hydrophobic layer has largest action. To demonstrate the tank-treading behavior of the vesicle, panels (b) 
and (d) provide the streamlines of the fluid velocity over the whole computational domain when the shear 
flow passes through the structure. The tank-treading motion of the structure is then observed, for instance,
the particle velocities in panel (d) indicate a clockwise tank-treading movement.

@@

\begin{figure}
\centering
\includegraphics[height=2in]{parabolic.eps}
  \caption{Vesicle under a parabolic flow where the strength of the flow $v_{max}=8.0$ and the control parameter $w=10$. The configuration is the state when $t=10000$. Red arrows are directors of particle velocities. The inset shows the mean $y$-position over time. 
  }
    \label{figure7}
\end{figure}

>>>>

Following the relaxation experiments of the Janus-vesicle, this section will focus on the behavior of 
Janus-vesicles under a number of flows. To extract physical quantities of the target structure using the
proposed model, the scaling laws and the dimensionless units are given as follows.
The length unit is scaled by the length of phospholipids $l=2.5$ nm which is set as the diameter of each 
Janus particle. The force is scaled from the interfacial tension $\gamma=4.11$ pN nm$^{-1}$ 
from ~\cite{Ryham16}. This also means that the energy unit is scaled by $1\ k_BT$. We then be able to
calculate the characteristic time scale $\tau = \mu l/\gamma = 0.61$ ns where the fluid viscosity $\mu=1$ cP.
With the same framework, \cite{Fu20} provides the bending rigidity $\kappa=8.51$ $k_BT$.
%
For the model parameters, the decay length of attraction $\rho = 2l = 5$ nm, the repulsion length scale is 
$\rho_0=0.5$, and the repulsion strength $M=4.0\ k_BT$.
The dimensionless shear rate is given by $\chi = \dot\gamma \tau$ where $\dot\gamma$ is the shear rate.

@@

To study the deformation of a Janus-vesicle under a shear flow using the proposed algorithm, 
we adopt a widely tested numerical simulation in both continuum and molecular dynamics models, single vesicle under a shear flow. The well known results indicate that the vesicle has tank-treading behavior when 
there is no viscosity contrast in both fluids inside and outside of the vesicle. Within the framework of the simulation setup, the proposed model provides a feature that the fluid viscosity is constant over the computational domain and it is capable of performing these simulations.

The centroid of the pre-relaxed $58$-body Janus vesicle is initially placed at the origin then the shear flow 
with a certain shear rate $\chi$ is then turned on. 
The snapshots of the simulation for single vesicle in a shear flow with a shear rate $\chi=0.0025$ are shown 
in Figure~\ref{figure3}.
Panels (a)-(b) show the initial shape obtained from the relaxation run and the deformed 
configuration of the Janus-vesicle after a period of time ($t=4000$) is in panels (c)-(d). 
The background color in panels (a) and (c) presented in the figure is the strength of the action due to the
hydrophobic attraction. From weak to strong action field, the color varies from blue to red. Clearly, the
hydrophobic layer has largest action. To demonstrate the tank-treading behavior of the vesicle, panels (b) 
and (d) provide the streamlines of the fluid velocity over the whole computational domain when the shear 
flow passes through the structure. The tank-treading motion of the structure is then observed, for instance,
the particle velocities in panel (d) indicate a clockwise tank-treading movement.

@@

\begin{figure}
\centering
\includegraphics[height=2in]{parabolic.eps}
  \caption{Vesicle under a parabolic flow where the strength of the flow $v_{max}=32.8$ nm ns$^{-1}$, $R_0 = 20$ nm,  and the control parameter $w=10$. The configuration is the state when $t=\{0, 4000, 8000\}$. Red curves are midplanes of three configurations. 
  }
    \label{figure7}
\end{figure}
